### 2022-05-26 chapters/04-chapter-4.tex
txs auto checkin

\begin{algorithm}[hbt!]
	\SetAlgorithmName{Algoritme}{Algoritme}
		\KwData{this text}
		\KwResult{how to write algorithm with \LaTeX2e }
		initialization\;
		\While{not at end of this document}{
			read current\;
			\eIf{understand}{
				go to next section\;
				current section becomes this one\;
			}{
				go back to the beginning of current section\;
			}
		}

	\caption{Algoritme pendeteksian regresi}\label{alg:regression-detection}
\end{algorithm}
\begin{algorithm}[hbt!]
	\SetAlgorithmName{Algoritme}{Algoritme}

>>>>

\begin{algorithm}[hbt!]
	\SetAlgorithmName{Algoritme}{Algoritme}

	\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
	\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
	\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
	\Input{A bitmap $Im$ of size $w\times l$}
	\Output{A partition of the bitmap}
	\BlankLine
	\caption{Algoritme pendeteksian regresi}\label{alg:regression-detection}
\end{algorithm}
\begin{algorithm}[hbt!]
	\SetAlgorithmName{Algoritme}{Algoritme}
